Promiscuous Speculation: When is it inappropriate to flaunt your guesses?

### 2022-12-03 paper.tex
Added spectre gadget example

{\Large stick example gadget from original spectre paper here}

@@

\cite{mosier2022}.
\cite{cats2022}
\section{Future Work}\label{sec:future}

>>>>

Consider the code snippet in figure \ref{fig:gadget}.
Assuming an attacker can control the value of the variable \texttt{x}, then the attacker can train the branch predictor to execute the access relative to \texttt{array1} which will allow an out-of-bounds access to speculatively execute.
The value so accessed will then be used to access data relative to \texttt{array2}, but scaled so that values map to separate cache lines.
Then the attacker can scan \texttt{array2}, timing the accesses, and by identifying which cache line returned fastest infer what the value was at the original out-of-bounds access.
This is the original gadget example from the Spectre paper but many more variations are possible as we explore below.

\begin{figure}[t]
  \begin{verbatim}
  if (x < array1_size)
    y = array2[array1[x] * 4096];\end{verbatim}
	\caption{Example of a Spectre \emph{gadget} reproduced from \cite{spectre}}
  \label{fig:gadget}
\end{figure}

@@

\textit{Axiomatic Hardware-Software Contracts for Security} presents 
\cite{mosier2022}

\cite{cats2022}
\section{Future Work}\label{sec:future}
